Vasseur \& Fox (2007) replication

### 2022-11-15 use_case/analysis_vasseur_fox.Rmd
Finish with McCann / Brose

---
title: "Community biomass and species richness temporal trends reveal contrasting assembly and disassembly processes in natural food-webs"
author: Alain Danet, Loubna El Madouri, Maud Mouchet, Elisa Thébault and Colin Fontaine
date: \today
output:
  bookdown::pdf_document2:
    fig_caption: true 
    keep_tex: true
    toc: true
    fontsize: 12pt
    geometry: margin=2cm
    number_sections: true
---

>>>>

---
title: "Vasseur \& Fox (2007) replication"
author: Alain Danet
date: \today
output:
  bookdown::pdf_document2:
    fig_caption: true 
    keep_tex: true
    toc: true
    fontsize: 12pt
    geometry: margin=2cm
    number_sections: true
---
